Gov 50 Final Project

### 2022-12-04 article.Rmd
j

```{r}
ATP_W70 <- read.csv("ATP_W70FromR.csv")
```

```{r}
ATP_W70 <- ATP_W70 |> mutate (Pray = case_when(SPIRIT2_a_W70 >=1 & SPIRIT2_a_W70 <= 4 ~ '1')) |> mutate(Scripture = case_when(SPIRIT2_b_W70 >=1 & SPIRIT2_b_W70 <= 4 ~ '1')) |> mutate (Meditate = case_when(SPIRIT1_a_W70 >=1 & SPIRIT1_a_W70 <= 4 ~ '1')) 
```

```{r}
ATP_W70 <- ATP_W70 |> mutate(Opinions_on_SD = case_when(COVIDCONG4_W70 == 1 ~ "Open", COVIDCONG4_W70 == 2 ~ "Open with restictions", COVIDCONG4_W70 == 3 ~ "Closed"))|> mutate (college_edu = ifelse(F_EDUCCAT == 1, "College", "Not College")) |> mutate (PARTY_affiliation = case_when(PARTY_W70 == 1 ~ "Republican", PARTY_W70 == 2 ~ "Democrat", PARTY_W70 == 3 ~ "Independent", PARTY_W70 == 4 ~ "Something else")) |> filter (PARTY_affiliation %in% c("Republican", "Democrat"))
```

##visualization 1
```{r}
Opinions <- ATP_W70 |> group_by( PARTY_affiliation, Opinions_on_SD) |> summarise(n= n()) |> mutate (prop = n/ sum(n)) |> drop_na( PARTY_affiliation, Opinions_on_SD)

@@

Opinions_diff_by_edu <- ATP_W70 |> filter (PARTY_affliation %in% c("Republican", "Democrat")) |> group_by(PARTY_affiliation, college_edu, Opinions_on_SD) |> summarise(n= n()) |> mutate (prop = n/ sum(n)) |> drop_na(Opinions_on_SD, PARTY_affiliation) |> select (-n)|> pivot_wider(names_from = PARTY_affiliation, values_from = prop) |> mutate (Diff_in_prop = Republican - Democrat)
knitr:: kable (Opinions_diff_by_edu)

Opinions_by_educ_plot <- Opinions_diff_by_edu|> ggplot(aes(x = Opinions_on_SD, y = Diff_in_prop, fill =  college_edu)) + geom_col(position = "dodge") + labs( Title = "opinions on what the operatings status of places of worship should be according to Party affiliation and college education")

Opinions_by_educ_plot
```

>>>>

```{r}
ATP_W70 <- read.csv("ATP_W70FromR.csv")
library(tidyverse)
```

```{r}
ATP_W70 <- ATP_W70 |> mutate (Pray = case_when(SPIRIT2_a_W70 >=1 & SPIRIT2_a_W70 <= 4 ~ '1')) |> mutate(Scripture = case_when(SPIRIT2_b_W70 >=1 & SPIRIT2_b_W70 <= 4 ~ '1')) |> mutate (Meditate = case_when(SPIRIT1_a_W70 >=1 & SPIRIT1_a_W70 <= 4 ~ '1')) |> mutate (spirtuality = ifelse (Pray == 1| Scripture == 1| Meditate == 1, "1", "0"))

```

```{r}
ATP_W70 <- ATP_W70 |> mutate(Opinions_on_SD = case_when(COVIDCONG4_W70 == 1 ~ "Open", COVIDCONG4_W70 == 2 ~ "Open with restictions", COVIDCONG4_W70 == 3 ~ "Closed"))|> mutate (college_edu = ifelse(F_EDUCCAT == 1, "College", "Not College")) |> mutate (PARTY_affiliation = case_when(PARTY_W70 == 1 ~ "Republican", PARTY_W70 == 2 ~ "Democrat", PARTY_W70 == 3 ~ "Independent", PARTY_W70 == 4 ~ "Something else")) |> mutate (Black = if_else(F_RACECMB == 2, "1", "0")) |> mutate(Ideology = case_when(F_IDEO > 0 & F_IDEO < 3 ~ "Conservative", F_IDEO == 3 ~ "Moderate", F_IDEO > 3 & F_IDEO < 5 ~ "Liberal"))

Opinions_final <- ATP_W70 |> drop_na(Opinions_on_SD) |> select(Opinions_on_SD, COVIDCONG4_W70, college_edu, PARTY_affiliation, Black, F_IDEO, Ideology, spirtuality) |> filter (PARTY_affiliation %in% c("Republican", "Democrat"))

Opinions_final  
```

##visualization 1
```{r}
Opinions <- Opinions_final |> group_by( PARTY_affiliation, Opinions_on_SD) |> summarise(n= n()) |> mutate (prop = n/ sum(n)) |> drop_na( PARTY_affiliation, Opinions_on_SD)

@@

Opinions_diff_by_edu <- Opinions_final |> filter (PARTY_affiliation %in% c("Democrat", "Republican")) |> group_by(PARTY_affiliation, college_edu, Opinions_on_SD) |> summarise(n= n()) |> mutate (prop = n/ sum(n)) |> pivot_wider(names_from = PARTY_affiliation, values_from = prop)

#|> drop_na(Opinions_on_SD, PARTY_affiliation) 
knitr:: kable (Opinions_diff_by_edu)

Opinions_by_educ_plot <- Opinions_diff_by_edu|> ggplot(aes(x = Opinions_on_SD, y = Democrat, fill =  college_edu)) + geom_col(position = "dodge") + labs( Title = "opinions on what the operatings status of places of worship should be according to Party affiliation and college education")

Opinions_by_educ_plot
```
```{r}

Opinions_diff_by_edu_rep <- Opinions_final |> filter (PARTY_affiliation %in% c("Democrat", "Republican")) |> group_by(PARTY_affiliation, college_edu, Opinions_on_SD) |> summarise(n= n()) |> mutate (prop = n/ sum(n)) |> select (-n)|> pivot_wider(names_from = PARTY_affiliation, values_from = prop)

#|> drop_na(Opinions_on_SD, PARTY_affiliation) 
knitr:: kable (Opinions_diff_by_edu_rep)

Opinions_by_educ_plot_rep <- Opinions_diff_by_edu_rep|> ggplot(aes(x = Opinions_on_SD, y = Republican, fill =  college_edu)) + geom_col(position = "dodge") + labs( Title = "opinions on what the operatings status of places of worship should be according to Party affiliation and college education")

Opinions_by_educ_plot_rep
```
```{r}
ATP_W70_TEST |> mutate(Opinions_on_SD_numeric = case_when(COVIDCONG4_W70 == 1 ~ "1", COVIDCONG4_W70 == 2 ~ "0", COVIDCONG4_W70 == 3 ~ "-1")) |> mutate (Party_binary = case_when(PARTY_W70 == 1 ~ "1", PARTY_W70 == 2 ~ "0")) |> select (Party_binary, PARTY_W70) 
```

```{r}
library(tidyverse)
ATP_W70_TEST <- ATP_W70 |> drop_na(COVIDCONG4_W70)

sing_Regression <- lm(Opinions_on_SD_numeric ~ party_binary, data = ATP_W70_TEST)
summary(sing_Regression)

```

```{r}
Mult_regression <- lm(Opinions_on_SD ~ party-binary + Black + college_edu + spirtuality, data = ATP_W70)
```
